### 2019-02-20 manuscript/introduction.tex
- fixing introduced bibtex missing/errors - compiled pdf

%B: this is highly preliminary, for your editing consideration.
The systematic search for traits which influence the rates at which species accumulate around the tree of life is at the productive confluence of drastic increases in the size of datasets and equally dramatic improvements in analytical methods \citep{maddison_2007,fitzjohn_2009,goldberg_2012,beaulieu_2015}. % some papers with big trees.
Many limitations impede our progress in identifying estimating trait-dependent differences in speciation and extinction rates \citep{maddison_2015, rabosky_2015}. % add Moore/Hoehna?
Nevertheless, the field has made steady advances in relaxing assumptions and addressing conceptual difficulties. %maybe add beaulieu_2015 here, instead
One limitation is the pervasive consideration of traits in isolation. 
For example, studies commonly aim to identify the effects of alternate states of a single trait on the diversification process. 
This is problematic, because the context in which traits occur can lead to complex interactions, perhaps with other traits that make up an organism or its environment.
Consequently, an obvious direction for improvement of trait-dependent diversification models ought to involve development of approaches that allow investigation of individual and joint effects of traits on diversification, as well as each other's state transitions.
Ideally, the initial application of such approaches ought to rely on well-sampled and studied traits, whose interactions are relatively clear, and which show a wide phylogenetic distribution. 
%B: We can then have a good prior, reliable data, and replicate the studies.
In this paper, we use two of the best studied traits in flowering plants, ploidy and breeding system, and demonstrate an approach to consider their individual and joint effects on diversification.

>>>>

%B: this is highly preliminary, for your editing consideration.
The systematic search for traits which influence the rates at which species accumulate around the tree of life is at the productive confluence of drastic increases in the size of datasets and equally dramatic improvements in analytical methods \citep{maddison_2007,fitzjohn_2009,goldberg_2012,beaulieu_2016}. % some papers with big trees.
Many limitations impede our progress in identifying estimating trait-dependent differences in speciation and extinction rates \citep{maddison_2014, rabosky_2015}. % add Moore/Hoehna?
Nevertheless, the field has made steady advances in relaxing assumptions and addressing conceptual difficulties. %maybe add beaulieu_2016 here, instead
One limitation is the pervasive consideration of traits in isolation. 
For example, studies commonly aim to identify the effects of alternate states of a single trait on the diversification process. 
This is problematic, because the context in which traits occur can lead to complex interactions, perhaps with other traits that make up an organism or its environment.
Consequently, an obvious direction for improvement of trait-dependent diversification models ought to involve development of approaches that allow investigation of individual and joint effects of traits on diversification, as well as each other's state transitions.
Ideally, the initial application of such approaches ought to rely on well-sampled and studied traits, whose interactions are relatively clear, and which show a wide phylogenetic distribution. 
%B: We can then have a good prior, reliable data, and replicate the studies.
In this paper, we use two of the best studied traits in flowering plants, ploidy and breeding system, and demonstrate an approach to consider their individual and joint effects on diversification.
